### 2020-05-26 writeup/setup.tex

\textbf{Notations.} For the sake of clarity, we denote the first task as the source task and last ($t$-th) task as the target task.

>>>>

\textbf{Notations.} We refer to the last ($t$-th) task as the target task and the first task as the source task when there are only two tasks.
When there is no ambiguity, we drop the subscript $t$ from $\te_t(\hat{\beta}_t^{\MTL})$ to $\te(\hat{\beta}_t^{\MTL})$ for simplicity.
We call $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ the covariate shift matrix.
%Same for $\hat{\beta}_t^{\STL}$.
